Draft

### 2019-09-06 draft.tex
1 equivalence, prop trunc 5 restructure a bit

\begin{titlepage}
\hypersetup{pageanchor=false}
\maketitle
\thispagestyle{empty}
\end{titlepage}
\hypersetup{pageanchor=true}
%Below is an example of the problem environment
\chapter{Type Theory}
\section{Introduction}
Type theory is a formal language and deductive system, that is self sufficient in the sense that it need not be formulated as a collection of axioms on top of some other formal system like First Order Logic, instead its deductive system can be built on top of its own formal language. 
\todo{longer sentence to check formating }

Central to Type Theory is the notion of \textit{Type}. Every term $a$ in Type Theory we come across, must lie in some type $A$, which we denote as $a : A$. Note that the relation $:$ is transitive, so $a : A$ and $A : B$ imply $a : B$. 
%This induces the cummulative hierarchy shape of the universe of types $\mathcal{U}$, wherein every level of the universe includes all lower levels and their types.

@@

\section{Type Construction Operations}
Let's have a look at some important type constructions.
\begin{itemize}
	\item Given types $A, B : \mathcal{U}$ we can define the type $A \rightarrow B$ of functions from $A$ to $B$. 
		We can use $\lambda$-abstraction to construct elements of this type. $\lambda x. \Phi$ lies in $A \rightarrow B$ iff for $a : A$ we have $\Phi[a/x] : B$. 
		For $f : A \rightarrow B$ and $a : A$ we have that the application of $f$ on $a$, denoted as $f(a)$ or $f\;a$, lies in $B$.
	\item Given some type $A : \mathcal{U}$ and a family of types $B$ over $A$, $B : A \rightarrow \mathcal{U}$, we have the type of dependent functions $$\prod_{a : A} B(a)$$
	where for $f : \prod_{a : A} B(a)$ and $x : A$ we have $f(x) : B(x)$. 
	As in the case of non-dependent functions, we can use lambda abstraction to construct elements of a dependently-typed function type.
	\item Given $A, B : \mathcal{U}$ we can define the product type $A \times B : \mathcal{U}$. 
	For $a : A$ and $b : B$ we have the pair $(a,b) : A \times B$. 
	We also have the projection functions 
	$$\mathtt{pr}_1 : A \times B \rightarrow A : (a,b) \mapsto a$$
	$$\mathtt{pr}_2 : A \times B \rightarrow B : (a,b) \mapsto b$$
	\item Given $A : \mathcal{U}$ and family of types $B$ over $A$, $B : A \rightarrow \mathcal{U}$, we can define the dependent pair type $$\sum_{a : A} B(a)$$
	Given $x : A$ and $b : B(x)$ we can construct the pair $(x,b) : \sum_{a : A} B(a)$. 
	We have two projection functions, similar to the case of the product type.
	\item Given $A, B : \mathcal{U}$ we can construct the coproduct type $A + B$. 
	We can construct elements of $A + B$ using the functions
	$$\mathtt{inl} : A \rightarrow A+B$$
	$$\mathtt{inr} : B \rightarrow A+B$$
	This induces the induction principle
	$$\mathtt{ind}_{A+B} : \prod_{C : A+B \rightarrow U} \Big(\prod_{a : A}C(\mathtt{inl}\;a)\Big) \rightarrow \Big(\prod_{b : A}C(\mathtt{inr}\;b)\Big) \rightarrow \prod_{x : A+ B}C(x)$$
	\item Given $x, y : A$ we have the \textbf{identity type} $x =_A y$. 
	An element of this type amounts to a proof that $x$ and $y$ are equal. 
	Say $x$ and $y$ are judgmentally equal. 
	This is captured by the element $\mathtt{idp}_x : x =_A y$. 
	The relevant induction principle describes how we can use elements of an identity type
	$$\mathtt{ind}_{=_{A}} : \prod_{C : \prod_{x,y : A} (x =_A y) \rightarrow \mathcal{U}} \Big( \prod_{x : A}C(x,x,\mathtt{idp}_x) \Big) \rightarrow \prod_{x,y : A} \prod_{(p : x =_A y)} C(x,y,p)$$
	The relevant computation gives us the judgmental equality 
	$$\mathtt{ind}_{=_A} (C,c,x,x,\mathtt{idp_x}) \equiv c\; x$$
	We can concatenate those paths whose domains and codomains allow for it. 
	Paths are equivalences. That is if $p : x = y$ is such a  path, we can provide its inverse $p^{-1}$ for which we have in turn a path between $p\cdot p^{-1}$ and $\mathtt{idp}_y$ and another one between $p^{-1}\cdot p$ and $\mathtt{idp}_x$. 
	\item For every type $A$ there is its \textbf{propositional truncation} $\| A \|$. 
	For every element $a : A$ there exists $|a| : \| A\|$. 
	For every $x, y : \| A\|$ we have $x = y$. 
	Given mere proposition $B$ and $f : A \rightarrow B$, the recursion principle gives us $g : \|A\| \rightarrow B$ such that $g(|a|) \equiv f(a)$ for all $a : A$.

\end{itemize}

\section{Important types}
\begin{defn}
We call a type $A$ a \textbf{mere proposition} if for every $a,b : A$ we have $a = b$.
\end{defn}

@@

\begin{defn}
We call a type $A$ \textbf{contractible} if there exists $a : A$ such that for all $x : A$ it holds that $x = a$.
\end{defn}

@@

\begin{defn}
For $B : A \rightarrow \mathcal{U}$, we call $X$ $B$\textbf{-null} if the map 
$$\lambda x. \lambda b.x : X \rightarrow (B(a) \rightarrow X)$$
is an equivalence for all $a : A$.

@@

In other words, Church's thesis assures us that for every $f : \mathbb{N} \rightarrow \mathbb{N}$ there exists some computable function that agrees with it on every input.
This holds true for partial functions too, since any one of them can be trivially extended to a total $(\mathbb{N} \rightarrow \mathbb{N})$ one for the purposes of Church's thesis.

@@

\begin{lem}\label{NisBnull}
$\mathbb{N}$ is $\lVert B \rVert$-null in $\mathcal{E}$.
\end{lem}
\begin{proof}
Given $a : A$ and $f : \lVert B\; a \rVert \rightarrow \mathbb{N}$ we need to prove that there exists unique $f' : \mathbf{1} \rightarrow \mathbb{N}$ through which $f$ factors, in the sense that $f = f' \circ g$, where $g : \lVert B\; a \rVert \rightarrow \mathbf{1}$ is the sole inhabitant of its function space. 
Functions with $\mathbf{1}$ as their domain are constant. 
We therefore need to find some $z : \mathbb{N}$ so that $\lambda\; \_.\; z$ is $f'$. 
To that end, we will use IP' which we've proven true in $\mathcal{E}$. 
We invoke it twice. 
In both times, the first three arguments shall be the same. 
The choice for the first argument, $a$, is evident. 
We provide the composition $f \circ \lVert\cdot\rVert : B\; a \rightarrow \mathbb{N}$ as the second argument. 
Constructing a witness for the third argument is easy. 
Finally, for argument $r$ we provide the odd $s_1$ and even $s_2$ subsequences of $a$, along with proofs that they are indeed subsequences of $a$ and we get hold of $z_1 : \mathbb{N}$ and $z_2 : \mathbb{N} $ respectively. 
Equality on $\mathbb{N}$ is decidable, therefore $(z_1 = z_2) + (z_1 \neq z_2)$ is provable.

@@

\section{B-nullification preserves coproducts}
\begin{lem}
In $\mathcal{E}$ if $C, D$ are $\lVert B \rVert$-null then so is $C + D$.
\end{lem}
\begin{proof}
We need to show that for $f : \lVert B\; a\rVert \rightarrow C+D$ there exists unique $f' : \mathbf{1} \rightarrow C+D$ such that $f = f' \circ e$, where $e : \lVert B\; a\rVert \rightarrow \mathbf{1}$ is the sole inhabitant of its function space. 
We define $$g : C + D \rightarrow \mathbf{2}$$ 
using components
$$g_C :\equiv \lambda\; \_.\; 0 : C \rightarrow \mathbf{2}$$
$$g_D :\equiv \lambda\; \_.\; 1 : D \rightarrow \mathbf{2}$$
Recall that in $\mathcal{E}$ we have access to a witness of IP' which takes the following arguments in the form of a 4-product
\begin{align*}
&a: &A
\\
&\bar{f}: &B\; a \rightarrow C+D
\\ &\_ :
\begin{split}
\bigg( \prod_{\bar{s} : \mathbf{2}^\mathbb{N}} \Big(\big(\prod_{n : \mathbb{N}} \bar{s}(n) = a(2 \cdot n)\big) \vee \big(\prod_{n : \mathbb{N}} \bar{s}(n) = a(2\cdot n +1)\big) \Big) \rightarrow \\
	\quad \Big(\prod_{n : \mathbb{N}}\bar{s}\; n = 0 \Big) \rightarrow  \sum_{z : \mathbf{2}} \prod_{b : B\; a} g(\bar{f}\; b) = z  \bigg)
\end{split}
\\
&r : & \sum_{s : \mathbf{2}^\mathbb{N}} \Big(\big(\prod_{n : \mathbb{N}} s(n) = a(2 \cdot n)\big) \vee \big(\prod_{n : \mathbb{N}} s(n) = a(2\cdot n +1)\big)
\end{align*}
and returns
$$\Big\lVert \sum_{z : \mathbf{2}} \prod_{b : B\; a} g(\bar{f}\; b) = z \Big\rVert$$
We provide this with the arguments required, where $\bar{f}$ is $f$ composed with the truncation map $|*| : B\; a \rightarrow \lVert B\; a\rVert$, to get a witness 
$$\bar{z} : \sum_{z : \mathbf{2}} \prod_{b : B\; a} g(\bar{f}\; b) = z$$ 
Note that we dropped the truncation since our goal is a mere proposition, therefore we can act as if we have an actual $\bar{z}$. 
Using $\bar{z}$ we can prove that
$$y : \sum_{z : \mathbf{2}} \prod_{b : \lVert B\; a\rVert} g(f\; b) = z$$
We can prove that 
$$y= 0 + y = 1$$ 
We use induction on this coproduct to prove our goal. 
Without loss of generality, we argue only for the case of $y = 0$. 
As a first step towards providing a candidate for $f'$, we will try to construct some $h : \lVert B\; a\rVert \rightarrow C$ such that $\mathtt{inl} \circ h = f$. 
\begin{center}
\begin{tikzcd}
                                                             & \mathbf{1} \arrow[rdd, "f'", dashed, bend left] \arrow[d, "h'"', dashed]              &                    &            \\
                                                             & C \arrow[rd, "\mathtt{inl}"]                                                          &                    &            \\
B\; a \arrow[rr, "\bar{f}"', bend right=49] \arrow[r, "|*|"] & \lVert B\;a\rVert \arrow[r, "f"] \arrow[u, "h", dashed] \arrow[uu, "e", bend left=49] & C+D \arrow[r, "g"] & \mathbf{2}
\end{tikzcd}
\end{center}
Let $b : \lVert B\; a\rVert$. 
First, note that we can prove 
$$\zeta : \prod_{a: C+D} \Big(\big(\sum_{c : C} \mathtt{inl}\; c = a\big) + \big( \sum_{d:D} \mathtt{inr}\; d = a \big) \Big)$$
by induction on $C+D$. 
We then take cases on 
$$\zeta (f\; b) : \big(\sum_{c : C} \mathtt{inl}\; c = f\; b\big) + \big( \sum_{d:D} \mathtt{inr}\; d = f\; b \big)$$
\begin{itemize}
	\item If $\bar{c} : \sum_{c : C} \mathtt{inl}\; c = f\; b$, we define $h\; b :\equiv \bar{c}$.
	Clearly $\mathtt{inl} \circ h = f$.
	\item If $\sum_{d : D} \mathtt{inl}\; d = f\; b$, then $g(f\;b) = 1$ but since $y=0$ we also have $g(f\;b) = 0$. Contradiction. 
	This case is resolved by Ex Falso.
\end{itemize}
Since $C$ is $\lVert B \rVert$-null, there exists $h' : \mathbf{1} \rightarrow C$ such that $h = h' \circ e$. 
Observe that $\mathtt{inl} \circ h' : \mathbf{1} \rightarrow C+D$, furthermore $(\mathtt{inl} \circ h') \circ e= f$. 
We have found a valid candidate for $f'$, what is left is to show it's unique. 
% We reduce this to showing that $\sum_{f' : \mathbf{1} \rightarrow C+D} f' \circ e = f$ is a mere proposition.

@@

We shall now have a look at the interpretation of LLPO in $\mathcal{E}_{\lVert B \rVert}$. 
Recall the full definition \ref{LLPO} of LLPO
$$\prod_{a : A}\lVert \mathtt{p_{odd}}(a.\mathtt{fst}) + \mathtt{p_{even}}(a.\mathtt{fst}) \rVert$$
where $$A :\equiv \sum_{a: \mathbf{2}^\mathbb{N}}\mathtt{atMost1one}\;a$$
Since $\mathtt{atMost1one}$ is formed using $\mathbb{N}$, $\mathbf{2}$, equality on naturals and $\mathbf{2}$, dependent sum and product, all of which are preserved under modalities, we have that the interpretation of $\mathtt{atMost1one}$ in $\mathcal{E}_{\lVert B \rVert}$ is the same type as in $\mathcal{E}$. 
Similarly the interpretations of $A$, $\mathtt{p_{odd}}$ and $\mathtt{p_{even}}$ are the same. 
Therefore, the interpretation of LLPO in $\mathcal{E}_{\lVert B \rVert}$ is the type 
$$\prod_{a : A}\mathcal{L}_{\lVert B \rVert}\;\lVert \mathtt{p_{odd}}(a.\mathtt{fst}) + \mathtt{p_{even}}(a.\mathtt{fst}) \rVert$$
in $\mathcal{E}$. 
We would like to have a witness of this type. 
Let $a : A$. 
We once again utilize our shorthand $B\; a \equiv \mathtt{p_{odd}}(a.\mathtt{fst}) + \mathtt{p_{even}}(a.\mathtt{fst})$. 
Note that $\mathcal{L}_{\lVert B \rVert}\;\lVert \mathtt{p_{odd}}(a.\mathtt{fst}) + \mathtt{p_{even}}(a.\mathtt{fst}) \rVert$ is $\lVert B \rVert$-null, which means that we have the following equivalence
$$\mathcal{L}_{\lVert B \rVert}\; \lVert B\;a\rVert \simeq \lVert B\; a \rVert \rightarrow \mathcal{L}_{\lVert B \rVert}\;\lVert B\; a \rVert$$
So it is enough to prove $\lVert B\; a \rVert \rightarrow \mathcal{L}_{\lVert B \rVert}\;\lVert B\; a \rVert$, for which we already have a witness in the form of the first datum of Definition \ref{modality_definition}, since $\mathcal{L}_{\lVert B \rVert}$ is a modality.

>>>>

\begin{titlepage}
\hypersetup{pageanchor=false}
\maketitle
\thispagestyle{empty}
\end{titlepage}
\hypersetup{pageanchor=true}
%Below is an example of the problem environment
\chapter{Type Theory}
\section{Introduction}
Type theory is a formal language and deductive system, that is self sufficient in the sense that it need not be formulated as a collection of axioms on top of some other formal system like First Order Logic, instead its deductive system can be built on top of its own formal language.

Central to Type Theory is the notion of \textit{Type}. Every term $a$ in Type Theory we come across, must lie in some type $A$, which we denote as $a : A$. 
%Note that the relation $:$ is transitive, so $a : A$ and $A : B$ imply $a : B$. 
%This induces the cummulative hierarchy shape of the universe of types $\mathcal{U}$, wherein every level of the universe includes all lower levels and their types.

@@

\section{Type Construction Operations}
Let's have a look at some important type constructions.
\begin{itemize}
	\item Given types $A, B : \mathcal{U}$ we can define the type $A \rightarrow B$ of functions from $A$ to $B$. 
		We can use $\lambda$-abstraction to construct elements of this type. $\lambda x. \Phi$ lies in $A \rightarrow B$ iff for $a : A$ we have $\Phi[a/x] : B$. 
		For $f : A \rightarrow B$ and $a : A$ we have that the application of $f$ on $a$, denoted as $f(a)$ or $f\;a$, lies in $B$.
	\item Given some type $A : \mathcal{U}$ and a family of types $B$ over $A$, $B : A \rightarrow \mathcal{U}$, we have the type of dependent functions $$\prod_{a : A} B(a)$$
	where for $f : \prod_{a : A} B(a)$ and $x : A$ we have $f(x) : B(x)$. 
	As in the case of non-dependent functions, we can use lambda abstraction to construct elements of a dependently-typed function type.
	\item Given $A, B : \mathcal{U}$ we can define the product type $A \times B : \mathcal{U}$. 
	For $a : A$ and $b : B$ we have the pair $(a,b) : A \times B$. 
	We also have the projection functions 
	$$\mathtt{pr}_1 : A \times B \rightarrow A : (a,b) \mapsto a$$
	$$\mathtt{pr}_2 : A \times B \rightarrow B : (a,b) \mapsto b$$
	\item Given $A : \mathcal{U}$ and family of types $B$ over $A$, $B : A \rightarrow \mathcal{U}$, we can define the dependent pair type $$\sum_{a : A} B(a)$$
	Given $x : A$ and $b : B(x)$ we can construct the pair $(x,b) : \sum_{a : A} B(a)$. 
	We have two projection functions, similar to the case of the product type.
	\item Given $A, B : \mathcal{U}$ we can construct the coproduct type $A + B$. 
	We can construct elements of $A + B$ using the functions
	$$\mathtt{inl} : A \rightarrow A+B$$
	$$\mathtt{inr} : B \rightarrow A+B$$
	This induces the induction principle
	$$\mathtt{ind}_{A+B} : \prod_{C : A+B \rightarrow U} \Big(\prod_{a : A}C(\mathtt{inl}\;a)\Big) \rightarrow \Big(\prod_{b : A}C(\mathtt{inr}\;b)\Big) \rightarrow \prod_{x : A+ B}C(x)$$
	\item Given $x, y : A$ we have the \textbf{identity type} $x =_A y$. 
	An element of this type amounts to a proof that $x$ and $y$ are equal. 
	Say $x$ and $y$ are judgmentally equal. 
	This is captured by the element $\mathtt{idp}_x : x =_A y$. 
	The relevant induction principle describes how we can use elements of an identity type
	$$\mathtt{ind}_{=_{A}} : \prod_{C : \prod_{x,y : A} (x =_A y) \rightarrow \mathcal{U}} \Big( \prod_{x : A}C(x,x,\mathtt{idp}_x) \Big) \rightarrow \prod_{x,y : A} \prod_{(p : x =_A y)} C(x,y,p)$$
	The relevant computation gives us the judgmental equality 
	$$\mathtt{ind}_{=_A} (C,c,x,x,\mathtt{idp_x}) \equiv c\; x$$
	We can concatenate those paths whose domains and codomains allow for it. 
	Paths are equivalences. That is if $p : x = y$ is such a  path, we can provide its inverse $p^{-1}$ for which we have in turn a path between $p\cdot p^{-1}$ and $\mathtt{idp}_y$ and another one between $p^{-1}\cdot p$ and $\mathtt{idp}_x$. 
\end{itemize}
	\begin{defn}
	We call a type $A$ a \textbf{mere proposition} or simply a \textbf{proposition}, if for every $a,b : A$ we have $a = b$.
	\end{defn}

@@

	\begin{defn}
	We call a type $A$ \textbf{contractible} if there exists $a : A$ such that for all $x : A$ it holds that $x = a$.\\
	Formally
	$$\mathtt{isContr}\; A :\equiv \sum_{x : A}\prod_{a :A}x=a$$
	\end{defn}

	\begin{defn}
	Given some map $f : A \rightarrow B$, a \textbf{fiber} of it over some point $y : B$ is
	$$\mathtt{fib}_f\; y :\equiv \sum_{x : A} \big(f(x) = y\big)$$
	\end{defn}

	\begin{defn}
	We say that a map $f : A\rightarrow B$ has \textbf{contractible fibers} if for every $b : B$, the type $\mathtt{fib}_f(b)$ is contractible.\\
	Formally, 
	$$ \mathtt{hasContrFibers}\; f : \equiv \prod_{b : B} \mathtt{isContr}(\mathtt{fib}_f\; b)$$
 	\end{defn}
 	One way to see this, albeit naive from a set-theoretic point of view, is that we require for every element of the codomain to have exactly one element of the domain mapped to it by $f$. 
 	Note that for any map $f$, the type $\mathtt{hasContrFibers(f)}$ is a mere proposition.

 	We form a notion of \textbf{equivalence of types} based on maps with contractible fibers. 
 	Whenever we have some $f : A\rightarrow B$ with contractible fibers, we say that the types $A$ and $B$ are equivalent and write $A \simeq B$. 
 	To motivate this, note that we can form $g : B \rightarrow A$ so that $f\circ g \sim \mathtt{id}_B$ and $g\circ f \sim \mathtt{id}_A$. 
 	So we can use a witness of one of the types to get one of the other. 
 	Furthermore, the equivalence of types we introduced just now is an equivalence relation on $\mathcal{U}$. 
 	More exposition on equivalence can be found in chapter 4 of \cite{hottbook}.

\section{Higher inductive types}
\begin{itemize}
	\item For every type $A : \mathcal{U}$ there exists its \textbf{propositional truncation} $\| A \|$. 
	We also have the truncation map $|\cdot| : A \rightarrow \lVert A \rVert$ so that for every element $a : A$ there exists $|a| : \| A\|$. 
	For every $x, y : \| A\|$ we have $x = y$.

	Given mere proposition $B$ and $f : A \rightarrow B$, the recursion principle gives us $g : \|A\| \rightarrow B$ such that $g(|a|) \equiv f(a)$ for all $a : A$.
	This recursion principle will prove itself an indispensable tool in the sections to come. 
	Whenever, in the midst of a proof, the current goal $B$ is a mere proposition and we have access to some witness $a : \lVert A \rVert$, we are allowed by the recursion principle to assume that we have $a' : A$ and use it to construct a proof of $B$.
\end{itemize}

@@

\begin{defn}\label{Bnull}
For $B : A \rightarrow \mathcal{U}$, we call $X$ $B$\textbf{-null} if the map 
$$\lambda x. \lambda b.x : X \rightarrow (B(a) \rightarrow X)$$
is an equivalence for all $a : A$.

@@

In other words, Church's thesis assures us that for every $f : \mathbb{N} \rightarrow \mathbb{N}$ there exists some computable function that agrees with it on every input.

@@

\section{Null types in E}
The proofs in this section are all about $\lVert B \rVert$-nullness i.e. equivalence between function types (see Definition \ref{Bnull}). 
Our approach in showing that some $F: C\rightarrow D$ is a map with contractible fibers, is to provide for any $d :D$ some $c :C$ such that $f(c) = d$ and then show that such an $c$ is unique, where $C,D$ are said function types. 
\begin{lem}\label{NisBnull}
$\mathbb{N}$ is $\lVert B \rVert$-null in $\mathcal{E}$.
\end{lem}
\begin{proof}
Given $a : A$ and $f : \lVert B\; a \rVert \rightarrow \mathbb{N}$ we need to prove that there exists unique $f' : \mathbf{1} \rightarrow \mathbb{N}$ through which $f$ factors, in the sense that $f = f' \circ g$, where $g : \lVert B\; a \rVert \rightarrow \mathbf{1}$ is the sole inhabitant of its function space. 
Functions with $\mathbf{1}$ as their domain are constant. 
We therefore need to find some $z : \mathbb{N}$ so that $\lambda\; \_.\; z$ is $f'$. 
To that end, we will use IP' which we've proven true in $\mathcal{E}$. 
We invoke it twice. 
In both times, the first three arguments shall be the same. 
The choice for the first argument, $a$, is evident. 
We provide the composition $f \circ \lVert\cdot\rVert : B\; a \rightarrow \mathbb{N}$ as the second argument. 
Constructing a witness for the third argument is easy. 
Finally, for argument $r$ we provide the odd $s_1$ and even $s_2$ subsequences of $a$, along with proofs that they are indeed subsequences of $a$ and we get hold of $z_1 : \mathbb{N}$ and $z_2 : \mathbb{N} $ respectively. 
Equality on $\mathbb{N}$ is decidable, therefore $(z_1 = z_2) + (z_1 \neq z_2)$ is provable.

@@

\begin{lem}
In $\mathcal{E}$ if $C, D$ are $\lVert B \rVert$-null then so is $C + D$.
\end{lem}
\begin{proof}
We need to show that for $f : \lVert B\; a\rVert \rightarrow C+D$ there exists unique $f' : \mathbf{1} \rightarrow C+D$ such that $f = f' \circ e$, where $e : \lVert B\; a\rVert \rightarrow \mathbf{1}$ is the sole inhabitant of its function space. 
We define $$g : C + D \rightarrow \mathbf{2}$$ 
using components
$$g_C :\equiv \lambda\; \_.\; 0 : C \rightarrow \mathbf{2}$$
$$g_D :\equiv \lambda\; \_.\; 1 : D \rightarrow \mathbf{2}$$
Recall that in $\mathcal{E}$ we have access to a witness of IP' which takes the following arguments in the form of a 4-product
\begin{align*}
&a: &A
\\
&\bar{f}: &B\; a \rightarrow C+D
\\ &\_ :
\begin{split}
\bigg( \prod_{\bar{s} : \mathbf{2}^\mathbb{N}} \Big(\big(\prod_{n : \mathbb{N}} \bar{s}(n) = a(2 \cdot n)\big) \vee \big(\prod_{n : \mathbb{N}} \bar{s}(n) = a(2\cdot n +1)\big) \Big) \rightarrow \\
	\quad \Big(\prod_{n : \mathbb{N}}\bar{s}\; n = 0 \Big) \rightarrow  \sum_{z : \mathbf{2}} \prod_{b : B\; a} g(\bar{f}\; b) = z  \bigg)
\end{split}
\\
&r : & \sum_{s : \mathbf{2}^\mathbb{N}} \Big(\big(\prod_{n : \mathbb{N}} s(n) = a(2 \cdot n)\big) \vee \big(\prod_{n : \mathbb{N}} s(n) = a(2\cdot n +1)\big)
\end{align*}
and returns
$$\Big\lVert \sum_{z : \mathbf{2}} \prod_{b : B\; a} g(\bar{f}\; b) = z \Big\rVert$$
We provide this with the arguments required, where $\bar{f}$ is $f$ composed with the truncation map $|*| : B\; a \rightarrow \lVert B\; a\rVert$, to get a witness 
$$\bar{z} : \sum_{z : \mathbf{2}} \prod_{b : B\; a} g(\bar{f}\; b) = z$$ 
Note that we dropped the truncation since our goal is a mere proposition, therefore we can act as if we have an actual $\bar{z}$. 
Using $\bar{z}$ we can prove that
$$y : \sum_{z : \mathbf{2}} \prod_{b : \lVert B\; a\rVert} g(f\; b) = z$$
We can prove that 
$$y= 0 + y = 1$$ 
We use induction on this coproduct to prove our goal. 
Without loss of generality, we argue only for the case of $y = 0$. 
As a first step towards providing a candidate for $f'$, we will try to construct some $h : \lVert B\; a\rVert \rightarrow C$ such that $\mathtt{inl} \circ h = f$. 
\begin{center}
\begin{tikzcd}
                                                             & \mathbf{1} \arrow[rdd, "f'", dashed, bend left] \arrow[d, "h'"', dashed]              &                    &            \\
                                                             & C \arrow[rd, "\mathtt{inl}"]                                                          &                    &            \\
B\; a \arrow[rr, "\bar{f}"', bend right=49] \arrow[r, "|*|"] & \lVert B\;a\rVert \arrow[r, "f"] \arrow[u, "h", dashed] \arrow[uu, "e", bend left=49] & C+D \arrow[r, "g"] & \mathbf{2}
\end{tikzcd}
\end{center}
Let $b : \lVert B\; a\rVert$. 
First, note that we can prove 
$$\zeta : \prod_{a: C+D} \Big(\big(\sum_{c : C} \mathtt{inl}\; c = a\big) + \big( \sum_{d:D} \mathtt{inr}\; d = a \big) \Big)$$
by induction on $C+D$. 
We then take cases on 
$$\zeta (f\; b) : \big(\sum_{c : C} \mathtt{inl}\; c = f\; b\big) + \big( \sum_{d:D} \mathtt{inr}\; d = f\; b \big)$$
\begin{itemize}
	\item If $\bar{c} : \sum_{c : C} \mathtt{inl}\; c = f\; b$, we define $h\; b :\equiv \bar{c}$.
	Clearly $\mathtt{inl} \circ h = f$.
	\item If $\sum_{d : D} \mathtt{inl}\; d = f\; b$, then $g(f\;b) = 1$ but since $y=0$ we also have $g(f\;b) = 0$. Contradiction. 
	This case is resolved by Ex Falso.
\end{itemize}
Since $C$ is $\lVert B \rVert$-null, there exists $h' : \mathbf{1} \rightarrow C$ such that $h = h' \circ e$. 
Observe that $\mathtt{inl} \circ h' : \mathbf{1} \rightarrow C+D$, furthermore $(\mathtt{inl} \circ h') \circ e= f$. 
We have found a valid candidate for $f'$, what is left is to show it's unique. 
% We reduce this to showing that $\sum_{f' : \mathbf{1} \rightarrow C+D} f' \circ e = f$ is a mere proposition.

@@

We shall now have a look at the interpretation of LLPO in $\mathcal{E}_{\lVert B \rVert}$. 
Recall the full definition \ref{LLPO} of LLPO
$$\prod_{a : A}\lVert \mathtt{p_{odd}}(a.\mathtt{fst}) + \mathtt{p_{even}}(a.\mathtt{fst}) \rVert$$
where $$A :\equiv \sum_{a: \mathbf{2}^\mathbb{N}}\mathtt{atMost1one}\;a$$
Since $\mathtt{atMost1one}$ is formed using $\mathbb{N}$, $\mathbf{2}$, equality on naturals and $\mathbf{2}$, dependent sum and product, all of which are preserved under modalities, we have that the interpretation of $\mathtt{atMost1one}$ in $\mathcal{E}_{\lVert B \rVert}$ is the same type as in $\mathcal{E}$. 
Similarly the interpretations of $A$, $\mathtt{p_{odd}}$ and $\mathtt{p_{even}}$ are the same. 
Therefore, the interpretation of LLPO in $\mathcal{E}_{\lVert B \rVert}$ is the type 
$$\prod_{a : A}\mathcal{L}_{\lVert B \rVert}\;\lVert \mathtt{p_{odd}}(a.\mathtt{fst}) + \mathtt{p_{even}}(a.\mathtt{fst}) \rVert$$
in $\mathcal{E}$. 
We would like to have a witness of this type. 
Let $a : A$. 
We once again utilize our shorthand $B\; a \equiv \mathtt{p_{odd}}(a.\mathtt{fst}) + \mathtt{p_{even}}(a.\mathtt{fst})$. 
Note that $\mathcal{L}_{\lVert B \rVert}\;\lVert B\; a \rVert$ is $\lVert B \rVert$-null, which means that we have the following equivalence
$$\mathcal{L}_{\lVert B \rVert}\; \lVert B\;a\rVert \simeq \lVert B\; a \rVert \rightarrow \mathcal{L}_{\lVert B \rVert}\;\lVert B\; a \rVert$$
So it is enough to prove $\lVert B\; a \rVert \rightarrow \mathcal{L}_{\lVert B \rVert}\;\lVert B\; a \rVert$, for which we already have a witness in the form of the first datum of Definition \ref{modality_definition}, since $\mathcal{L}_{\lVert B \rVert}$ is a modality.
